Bayesian Hierarchical Modeling: An Introduction and Reassessment

### 2022-06-29 C - Tutorial Normal Model Rstan/Online Supplement C - Bayesian Hierarchical Modeling in rstan.Rmd
Improvements

- For the document layout: *rmarkdown* [Version 1.16; @R-rmarkdown], *papaja* [Version 0.1.0.9842; @R-papaja], *knitr* [Version 1.25; @R-knitr], *kableExtra* [Version 1.1.0; @R-kableExtra]
- For data structuring: *LaplacesDemon* [Version 16.1.4; @R-LaplacesDemon], *plyr* [Version 1.8.4; @R-plyr], *dplyr* [Version 0.8.3; @R-dplyr], *readr* [Version 1.3.1; @R-readr]
- To fit the model: *rstan* [Version 2.19.2; @R-rstan]
- For the visualization of the results: *lattice* [Version 0.20.38; @R-lattice], *ggplot2* [Version 3.3.2; @R-ggplot2], *Rmisc* [Version 1.5; @R-Rmisc], *devtools* [Version 2.2.1; @R-devtools], *gghalves* [Version 0.1.0; @R-gghalves], *bayesplot* [Version 1.7.1; @R-bayesplot], *brms* [Version 2.13.0; @R-brms_a; @R-brms_b], *gridExtra* [Version 2.3; @R-gridExtra], *tibble* [Version 3.0.2; @R-tibble]
- For model comparison: *bridgesamping* [Version 1.0.0; @R-bridgesampling]

>>>>

- For the document layout: *rmarkdown* [Version 1.16; @R-rmarkdown], *papaja* [Version 0.1.0.9842; @R-papaja], *knitr* [Version 1.25; @R-knitr], *kableExtra* [Version 1.1.0; @R-kableExtra]
- For data structuring: *LaplacesDemon* [Version 16.1.4; @R-LaplacesDemon], *plyr* [Version 1.8.4; @R-plyr], *dplyr* [Version 0.8.3; @R-dplyr], *readr* [Version 1.3.1; @R-readr], *truncnorm* [Version 1.0.8; @R-truncnorm]
- To fit the model: *rstan* [Version 2.19.2; @R-rstan]
- For the visualization of the results: *lattice* [Version 0.20.38; @R-lattice], *ggplot2* [Version 3.3.2; @R-ggplot2], *Rmisc* [Version 1.5; @R-Rmisc], *devtools* [Version 2.2.1; @R-devtools], *gghalves* [Version 0.1.0; @R-gghalves], *bayesplot* [Version 1.7.1; @R-bayesplot], *brms* [Version 2.13.0; @R-brms_a; @R-brms_b], *gridExtra* [Version 2.3; @R-gridExtra], *ggridges* [Version 0.5.3; @R-ggridges], *ggbeeswarm* [Version 0.6.0; @R-ggbeeswarm], *tibble* [Version 3.0.2; @R-tibble]
- For model comparison: *bridgesamping* [Version 1.0.0; @R-bridgesampling]

### 2022-06-29 D - Tutorial Normal Model brms/Online Supplement D - Bayesian Hierarchical Modeling in brms.Rmd
Improvements

---
title             : "Online Supplement D: Bayesian Hierarchical Modeling in brms"
author            : "Myrthe Veenman"
bibliography      : ["r-references.bib"]

@@

|    This online supplement provides a tutorial on Bayesian Hierarchical models (BHM) in `brms` [@R-brms_a; @R-brms_b]. In addition, it contains information about the Number Classification Task that could not be included in the paper. As `brms` runs on `Stan` [@carpenter2017stan], it is very similar to `rstan` [@R-rstan]. However, there are some differences that will be discussed in this tutorial. Only the fit of the full model will be shown as the fitting the others should follow logically from this tutorial. Technical details, such as explanations of statistical terms (e.g., $\hat{R}$), will not be discussed here but can be found in the paper. In concrete, the tutorial will cover the following:

@@

- For the document layout: *rmarkdown* [Version 1.16; @R-rmarkdown], *papaja* [Version 0.1.0.9842; @R-papaja], *knitr* [Version 1.25; @R-knitr], *kableExtra* [Version 1.1.0; @R-kableExtra]
- For data structuring: *LaplacesDemon* [Version 16.1.4; @R-LaplacesDemon], *plyr* [Version 1.8.4; @R-plyr], *dplyr* [Version 0.8.3; @R-dplyr], *readr* [Version 1.3.1; @R-readr], *truncnorm* [Version 1.0.8; @truncnorm]
- To fit the model and for model comparison: *brms* [Version 2.13.0; @R-brms_a; @R-brms_b]
- For the visualization of the results: *lattice* [Version 0.20.38; @R-lattice], *ggplot2* [Version 3.3.2; @R-ggplot2], *Rmisc* [Version 1.5; @R-Rmisc], *devtools* [Version 2.2.1; @R-devtools], *gghalves* [Version 0.1.0; @R-gghalves], *bayesplot* [Version 1.7.1; @R-bayesplot], *gridExtra* [Version 2.3; @R-gridExtra], *ggridges* [Version 0.5.3; @ggridges], *ggbeeswarm* [Version 0.6.0; @ggbeeswarm], *tibble* [Version 3.0.2; @R-tibble]

>>>>

---
title             : "Online Supplement D: Bayesian Hierarchical Modeling in brms"
author            : " "
bibliography      : ["r-references.bib"]

@@

|    This online supplement provides a tutorial on Bayesian Hierarchical models (BHM) in `brms` [@R-brms_a; @R-brms_b]. In addition, it contains information about the digit classification task that could not be included in the paper. As `brms` runs on `Stan` [@carpenter2017stan], it is very similar to `rstan` [@R-rstan]. However, there are some differences that will be discussed in this tutorial. Only the fit of the full model will be shown as the fitting the others should follow logically from this tutorial. Technical details, such as explanations of statistical terms (e.g., $\hat{R}$), will not be discussed here but can be found in the paper. In concrete, the tutorial will cover the following:

@@

- For the document layout: *rmarkdown* [Version 1.16; @R-rmarkdown], *papaja* [Version 0.1.0.9842; @R-papaja], *knitr* [Version 1.25; @R-knitr], *kableExtra* [Version 1.1.0; @R-kableExtra]
- For data structuring: *LaplacesDemon* [Version 16.1.4; @R-LaplacesDemon], *plyr* [Version 1.8.4; @R-plyr], *dplyr* [Version 0.8.3; @R-dplyr], *readr* [Version 1.3.1; @R-readr], *truncnorm* [Version 1.0.8; @R-truncnorm]
- To fit the model and for model comparison: *brms* [Version 2.13.0; @R-brms_a; @R-brms_b]
- For the visualization of the results: *lattice* [Version 0.20.38; @R-lattice], *ggplot2* [Version 3.3.2; @R-ggplot2], *Rmisc* [Version 1.5; @R-Rmisc], *devtools* [Version 2.2.1; @R-devtools], *gghalves* [Version 0.1.0; @R-gghalves], *bayesplot* [Version 1.7.1; @R-bayesplot], *gridExtra* [Version 2.3; @R-gridExtra], *ggridges* [Version 0.5.3; @R-ggridges], *ggbeeswarm* [Version 0.6.0; @R-ggbeeswarm], *tibble* [Version 3.0.2; @R-tibble]

### 2022-06-29 E - Tutorial Log-Normal Model Rstan/Online Supplement E - Bayesian Hierarchical Modeling in rstan - Log Model.Rmd
Improvements

---
title             : "Online Supplement E: Bayesian Hierarchical Modeling in rstan - Log Model"
author            : "Myrthe Veenman" 
bibliography      : ["r-references.bib"]
header-includes   :
   - \usepackage{bm}
   - \usepackage{amsmath}
   - \usepackage{setspace}
   - \usepackage{xcolor}
   - \definecolor{mypink}{RGB}{255, 230, 255}
   - \usepackage{todonotes}
   - \usepackage{graphicx}
   - \usepackage{float}

@@

|    This online supplement provides a tutorial on log-normal Bayesian Hierarchical models (BHM) in `rstan` [@R-rstan]. In addition, it contains information about the Number Classification Task that could not be included in the paper. Only the fit of the full model will be shown as the fitting the others should follow logically from this tutorial. Technical details, such as explanations of statistical terms (e.g., $\hat{R}$), will not be discussed here but can be found in the paper. This tutorial will cover the following:

@@

- For the document layout: *rmarkdown* [Version 1.16; @R-rmarkdown], *papaja* [Version 0.1.0.9842; @R-papaja], *knitr* [Version 1.25; @R-knitr], *kableExtra* [Version 1.1.0; @R-kableExtra]
- For data structuring: *LaplacesDemon* [Version 16.1.4; @R-LaplacesDemon], *plyr* [Version 1.8.4; @R-plyr], *dplyr* [Version 0.8.3; @R-dplyr], *readr* [Version 1.3.1; @R-readr]
- To fit the model: *rstan* [Version 2.19.2; @R-rstan]
- For the visualization of the results: *lattice* [Version 0.20.38; @R-lattice], *ggplot2* [Version 3.3.2; @R-ggplot2], *Rmisc* [Version 1.5; @R-Rmisc], *devtools* [Version 2.2.1; @R-devtools], *gghalves* [Version 0.1.0; @R-gghalves], *bayesplot* [Version 1.7.1; @R-bayesplot], *brms* [Version 2.13.0; @R-brms_a; @R-brms_b], *gridExtra* [Version 2.3; @R-gridExtra], *tibble* [Version 3.0.2; @R-tibble]
- For model comparison: *bridgesamping* [Version 1.0.0; @R-bridgesampling]

>>>>

---
title             : "Online Supplement E: Bayesian Hierarchical Modeling in rstan - Log Model"
author            : " " 
bibliography      : ["r-references.bib"]
header-includes   :
   - \usepackage{bm}
   - \usepackage{amsmath}
   - \usepackage{setspace}
   - \usepackage{xcolor}
   - \definecolor{mypink}{RGB}{255, 230, 255}
   - \usepackage{todonotes}
   - \usepackage{graphicx}
   - \usepackage{float}

@@

|    This online supplement provides a tutorial on log-normal Bayesian Hierarchical models (BHM) in `rstan` [@R-rstan]. In addition, it contains information about the digit classification task that could not be included in the paper. Only the fit of the full model will be shown as the fitting the others should follow logically from this tutorial. Technical details, such as explanations of statistical terms (e.g., $\hat{R}$), will not be discussed here but can be found in the paper. This tutorial will cover the following:

@@

- For the document layout: *rmarkdown* [Version 1.16; @R-rmarkdown], *papaja* [Version 0.1.0.9842; @R-papaja], *knitr* [Version 1.25; @R-knitr], *kableExtra* [Version 1.1.0; @R-kableExtra]
- For data structuring: *LaplacesDemon* [Version 16.1.4; @R-LaplacesDemon], *plyr* [Version 1.8.4; @R-plyr], *dplyr* [Version 0.8.3; @R-dplyr], *readr* [Version 1.3.1; @R-readr], *truncnorm* [Version 1.0.8; @R-truncnorm]
- To fit the model: *rstan* [Version 2.19.2; @R-rstan]
- For the visualization of the results: *lattice* [Version 0.20.38; @R-lattice], *ggplot2* [Version 3.3.2; @R-ggplot2], *Rmisc* [Version 1.5; @R-Rmisc], *devtools* [Version 2.2.1; @R-devtools], *gghalves* [Version 0.1.0; @R-gghalves], *bayesplot* [Version 1.7.1; @R-bayesplot], *brms* [Version 2.13.0; @R-brms_a; @R-brms_b], *gridExtra* [Version 2.3; @R-gridExtra], *ggbeeswarm* [Version 0.6.0; @R-ggbeeswarm], *tibble* [Version 3.0.2; @R-tibble]
- For model comparison: *bridgesamping* [Version 1.0.0; @R-bridgesampling]

### 2022-06-29 F - Tutorial Log-Normal Model brms/Online Supplement F - Bayesian Hierarchical Modeling in brms - Log Model.Rmd
Improvements

---
title             : "Online Supplement F: Bayesian Hierarchical Modeling in brms - Log Model"
author            : "Myrthe Veenman"
bibliography      : ["r-references.bib"]

@@

|    This online supplement provides a tutorial on log-normal Bayesian Hierarchical models (BHM) in `brms` [@R-brms_a; @R-brms_b]. In addition, it contains information about the Number Classification Task that could not be included in the paper. As `brms` runs on `Stan` [@carpenter2017stan], it is very similar to `rstan` [@R-rstan]. However, there are some differences that will be discussed in this tutorial. Only the fit of the full model will be shown as the fitting the others should follow logically from this tutorial. Technical details, such as explanations of statistical terms (e.g., $\hat{R}$), will not be discussed here but can be found in the paper. In concrete, the tutorial will cover the following:

@@

\scriptsize 
```{r traceplotsd, }
# Show trace plot for one sd parameter 
tr2 <- traceplotfunc(parameter = "sd_sub1__side", title = expression(~sigma[~beta]))
tr2 <- tr2 + theme(legend.position = "none")
tr3 <- traceplotfunc(parameter = "sd_sub1__dif1", title = expression(~sigma[~delta[~7]]))
tr3 <- tr3 + theme(legend.position = "none")
tr4 <- traceplotfunc(parameter = "sd_sub1__dif2", title = expression(~sigma[~delta[~6]]))
tr4 <- tr4 + theme(legend.position = "none")
tr5 <- traceplotfunc(parameter = "sd_sub1__dif3", title = expression(~sigma[~delta[~4]]))
tr5 <- tr5 + theme(legend.position = "none")
tr6 <- traceplotfunc(parameter = "sd_sub1__dif4", title = expression(~sigma[~delta[~3]]))
legendtr <- cowplot::get_legend(tr6)
tr6 <- tr6 + theme(legend.position = "none")

>>>>

---
title             : "Online Supplement F: Bayesian Hierarchical Modeling in brms - Log Model"
author            : " "
bibliography      : ["r-references.bib"]

@@

|    This online supplement provides a tutorial on log-normal Bayesian Hierarchical models (BHM) in `brms` [@R-brms_a; @R-brms_b]. In addition, it contains information about the digit classification task that could not be included in the paper. As `brms` runs on `Stan` [@carpenter2017stan], it is very similar to `rstan` [@R-rstan]. However, there are some differences that will be discussed in this tutorial. Only the fit of the full model will be shown as the fitting the others should follow logically from this tutorial. Technical details, such as explanations of statistical terms (e.g., $\hat{R}$), will not be discussed here but can be found in the paper. In concrete, the tutorial will cover the following:

@@

\scriptsize 
```{r traceplotsd, show = FALSE, echo = FALSE}
# Show trace plot for one sd parameter 
tr2 <- traceplotfunc(parameter = "sd_sub1__side", title = expression(~sigma[~beta]))
tr2 <- tr2 + theme(legend.position = "none")
tr3 <- traceplotfunc(parameter = "sd_sub1__dif1", title = expression(~sigma[~delta[~7]]))
tr3 <- tr3 + theme(legend.position = "none")
tr4 <- traceplotfunc(parameter = "sd_sub1__dif2", title = expression(~sigma[~delta[~6]]))
tr4 <- tr4 + theme(legend.position = "none")
tr5 <- traceplotfunc(parameter = "sd_sub1__dif3", title = expression(~sigma[~delta[~4]]))
tr5 <- tr5 + theme(legend.position = "none")
tr6 <- traceplotfunc(parameter = "sd_sub1__dif4", title = expression(~sigma[~delta[~3]]))
legendtr <- cowplot::get_legend(tr6)
tr6 <- tr6 + theme(legend.position = "none")

### 2022-06-29 manuscript.Rmd
Improvements

- Document layout: *rmarkdown* [Version 1.16; @R-rmarkdown], *papaja* [Version 0.1.0.9842; @R-papaja], *knitr* [Version 1.25; @R-knitr], *kableExtra* [Version 1.1.0; @R-kableExtra]
- Data analysis and cleaning: *LaplacesDemon* [Version 16.1.4; @R-LaplacesDemon], *plyr* [Version 1.8.4; @R-dplyr; @R-plyr], *dplyr* [Version 0.8.3; @R-dplyr], *readr* [Version 1.3.1; @R-readr], *crch* [Version 1.0.4; @R-crch_a; @R-crch_b; @R-crch_c; @R-crch_d], *foreign* [Version 0.8.71; @R-foreign], *Matrix* [Version 1.2.17; @R-Matrix], *tidyr* [Version 1.0.0; @R-tidyr]
- Model fit and comparison: *rstan* [Version 2.19.2; @R-rstan], *brms* [Version 2.13.0; @R-brms_a; @R-brms_b], *BayesFactor* [Version 0.9.12.4.2; @R-BayesFactor], *bridgesampling* [Version 1.0.0; @R-bridgesampling]
- Visualization: *coda* [Version 0.19.3; @R-coda], *lattice* [Version 0.20.38; @R-lattice], *ggplot2* [Version 3.3.2; @R-ggplot2], *Rmisc* [Version 1.5; @R-Rmisc], *devtools* [Version 2.2.1; @R-devtools], *gghalves* [Version 0.1.0; @R-gghalves], *bayesplot* [Version 1.7.1; @R-bayesplot], *gridExtra* [Version 2.3; @R-gridExtra], *tibble* [Version 3.0.2; @R-tibble], *ggmcmc* [Version 1.4.1; @R-ggmcmc], *cowplot* [Version 1.0.0; @R-cowplot], *ggridges* [Version 0.5.1; @R-ggridges], *circlize* [Version 0.4.9; @R-circlize], *StanHeaders* [Version 2.19.0; @R-StanHeaders], *unikn* [Version 0.2.0; @R-unikn]
- Other: *Rcpp* [Version 1.0.3; @R-Rcpp_a; @R-Rcpp_b], *usethis* [Version 1.5.1; @R-usethis]

>>>>

- Document layout: *rmarkdown* [Version 1.16; @R-rmarkdown], *papaja* [Version 0.1.0.9842; @R-papaja], *knitr* [Version 1.25; @R-knitr], *kableExtra* [Version 1.1.0; @R-kableExtra]
- Data analysis and cleaning: *LaplacesDemon* [Version 16.1.4; @R-LaplacesDemon], *plyr* [Version 1.8.4; @R-dplyr; @R-plyr], *dplyr* [Version 0.8.3; @R-dplyr], *readr* [Version 1.3.1; @R-readr], *crch* [Version 1.0.4; @R-crch_a; @R-crch_b; @R-crch_c; @R-crch_d], *foreign* [Version 0.8.71; @R-foreign], *Matrix* [Version 1.2.17; @R-Matrix], *tidyr* [Version 1.0.0; @R-tidyr], *truncnorm* [Version 1.0.8; @R-truncnorm] 
- Model fit and comparison: *rstan* [Version 2.19.2; @R-rstan], *brms* [Version 2.13.0; @R-brms_a; @R-brms_b], *BayesFactor* [Version 0.9.12.4.2; @R-BayesFactor], *bridgesampling* [Version 1.0.0; @R-bridgesampling]
- Visualization: *coda* [Version 0.19.3; @R-coda], *lattice* [Version 0.20.38; @R-lattice], *ggplot2* [Version 3.3.2; @R-ggplot2], *Rmisc* [Version 1.5; @R-Rmisc], *devtools* [Version 2.2.1; @R-devtools], *gghalves* [Version 0.1.0; @R-gghalves], *bayesplot* [Version 1.7.1; @R-bayesplot], *gridExtra* [Version 2.3; @R-gridExtra], *tibble* [Version 3.0.2; @R-tibble], *ggmcmc* [Version 1.4.1; @R-ggmcmc], *cowplot* [Version 1.0.0; @R-cowplot], *ggridges* [Version 0.5.1; @R-ggridges], *circlize* [Version 0.4.9; @R-circlize], *StanHeaders* [Version 2.19.0; @R-StanHeaders], *unikn* [Version 0.2.0; @R-unikn], *ggbeeswarm* [Version 0.6.0; @R-ggbeeswarm]
- Other: *Rcpp* [Version 1.0.3; @R-Rcpp_a; @R-Rcpp_b], *usethis* [Version 1.5.1; @R-usethis]
